Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-11-03 aggregation/agg-JIE.tex
Some morning work

@@

  \input{../publication/publication-example}

>>>>

\subsection{Interpreting the Foreground}

The foreground of an LCA study is a collection of nodes that represent points in the inventory model where flows are exchanged.  The foreground matrix $A_f$ describes in precise terms what components are included in the product system and how they connect to one another.  The foreground is modelled as a weighted directed graph in which there is a 1:1 correspondence between nodes and product flows.  The foreground matrix $A_f$ reports the adjacency and weights of edges in the graph, and thus describes the relationships among these nodes.  These nodes typically represent unit processes, but they can also indicate exchanges across an implicit system boundary that encloses the foreground.  Generally, the foreground matrix $A_f$ can represent any process-flow model with a 1:1 correspondence between processes and flows, i.e. any allocated supply-and-use table, but some fundamental designs are common.  Some simple foreground models are shown in the supplementary materials.

@@

  \input{../manuscript/publication-example}

### 2017-11-03 aggregation/agg-foreground.tex
Private disclosure work
Some morning work

\subsection{Interpreting the Foreground}

The foreground of an LCA study is a collection of nodes that represent points in the inventory model where flows are exchanged.  The foreground matrix $A_f$ describes in precise terms what components are included in the product system and how they connect to one another.  The foreground is modelled as a weighted directed graph in which there is a 1:1 correspondence between nodes and product flows.  The foreground matrix $A_f$ reports the adjacency and weights of edges in the graph, and thus describes the relationships among these nodes.  These nodes typically represent unit processes, but they can also indicate exchanges across an implicit system boundary that encloses the foreground.

A reviewer with access to items \ref{itm:fg} and \ref{itm:af} in the disclosure would be able to construct $A_f$ and automatically create a process-flow diagram, annotated with information about each node.  Generally, the foreground matrix $A_f$ can represent any process-flow model with a 1:1 correspondence between processes and flows, i.e. any allocated supply-and-use table, but some fundamental designs are common.  Some simple foreground models are shown in Figure~\ref{fig:fragments}.

@@

A typical PSM may contain multiple fragmentary elements that are interconnected.  An example of foreground composed of several fragments is illustrated in Figure~\ref{fig:fragments}(d).  Here, the nodes labeled 1--5 represent one fragment, which generates the foreground's canonical reference flow $\tilde{y}$. This fragment requires two interior flows from separate fragments ($y_0$ and $y_1$), and has two unconnected flows (4 and 5).  The reference $y_0$ is supplied by a second fragment, made up of nodes 6-8.  The reference $y_1$ is supplied by another fragment made of only one node (9). The reference flow $y_1$ is consumed in two different places by the other fragments.

>>>>

\section{Foreground Configurations}

Figure~\ref{fig:fragments} illustrates the structure of some basic foreground configurations.  Most product system models would include many of these elements mixed together.  A reviewer with access to items \ref{itm:fg} and \ref{itm:af} in the disclosure would be able to construct $A_f$ and automatically create a process-flow diagram, annotated with information about each node.

@@

A typical PSM may contain multiple modules or fragments that are interconnected.  An example of foreground composed of several fragments is illustrated in Figure~\ref{fig:fragments}(d).  Here, the nodes labeled 1--5 represent one fragment, which generates the foreground's canonical reference flow $\tilde{y}$. This fragment requires two interior flows from separate fragments ($y_0$ and $y_1$), and has two unconnected flows (4 and 5).  The reference $y_0$ is supplied by a second fragment, made up of nodes 6-8.  The reference $y_1$ is supplied by another fragment made of only one node (9). The reference flow $y_1$ is consumed in two different places by the other fragments.

### 2017-11-03 aggregation/agg-pagg.tex
Some morning work

The $A_d$ and $B_f$ matrices are then partitioned into two components that sum to the original:
\begin{equation}\begin{aligned}
  A_d =\; & A_{d,pub} + A_{d,priv} \\
  B_f =\; & B_{f,pub} + B_{f,priv}
  \label{eqn:partition}
  \end{aligned}
  \end{equation}
This is illustrated in Fig.~\ref{fig:private}b.  Substituted back into Eq.~\ref{eqn:study}, the private portions are aggregated into a private life cycle inventory vector $\mathbf{b}_{priv}$, while the public portions remain disaggregated:
\begin{align}
  s =\; & \mathbf{e}^T\times\left((B_{f,pub} + B_{f,priv}) + B_x\times (A_{d,pub} + A_{d,priv})\right)\times\tilde{\mathbf{x}}\\
  =\; & \mathbf{e}^T\times\left((B_{f,pub} + B_x\times A_{d,pub})\times\tilde{\mathbf{x}} + \mathbf{b}_{priv}\right)\label{eqn:private}\\
  \mathbf{b}_{priv} =\; & (B_{f,priv} + B_x\times A_{d,priv})\times \tilde{\mathbf{x}}
\end{align}
Any foreground nodes that are completely contained within the private partition can be omitted from the disclosed foreground.  The aggregation result can then be included as a separate foreground node with a unit weight, and the aggregated inventory vector included as the corresponding column of $B_f$.  This is illustrated in Fig.~\ref{fig:private}c.  The

>>>>

The $A_d$ and $B_f$ matrices are then partitioned into two components that sum to the original:
\begin{equation}\begin{aligned}
  A_d =\; & A_{d,pub} + A_{d,priv} \\
  B_f =\; & B_{f,pub} + B_{f,priv}
  \label{eqn:partition}
  \end{aligned}
  \end{equation}
This is illustrated in Fig.~\ref{fig:private}b.  Substituted back into Eq.~\ref{eqn:study}, the private portions are aggregated into a private life cycle inventory vector $\mathbf{b}_{priv}$, while the public portions remain disaggregated:
\begin{align}
  s =\; & \mathbf{e}^T\times\left((B_{f,pub} + B_{f,priv}) + B_x\times (A_{d,pub} + A_{d,priv})\right)\times\tilde{\mathbf{x}}\\
  =\; & \mathbf{e}^T\times\left((B_{f,pub} + B_x\times A_{d,pub})\times\tilde{\mathbf{x}} + \mathbf{b}_{priv}\right)\label{eqn:private}\\
  \mathbf{b}_{priv} =\; & (B_{f,priv} + B_x\times A_{d,priv})\times \tilde{\mathbf{x}}
\end{align}
Any foreground nodes that are completely contained within the private partition can be omitted from the disclosed foreground.  The aggregation result can then be included as a separate foreground node with a unit weight, and the aggregated inventory vector included as the corresponding column of $B_f$.  This is illustrated in Fig.~\ref{fig:private}c.

The author may relax the disclosure constraints by reporting the locations of some or all non-zero entries in $A_{d,priv}$ and $B_{f,priv}$ but not disclosing their values. This would enable a reader to understand \emph{that} a certain background process or emission was included in the model, but not to know \emph{how much} was included.
